Balsa: A Compact Line Notation Based on SMILES

### 2022-07-03 manuscript.tex
Adds figure for stack. Closes #18
Adds figure for bridge bonds compatibility. Closes #19

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a stack. At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Stack for branches.}
    \label{fig:branches-stack}
\end{figure}

Additional modifications allow bridge bonds to be tested for \textit{compatibility}. Compatibility is tested by comparing the attributes of each bridge bond. This test has three parts:

@@

A workflow modification allows bridge bonds to be compared for compatibility (Figure~\ref{fig:testing-bridge-bond-compatibility}). A 100-element array is used to maintain state. The first occurrence of a bridge causes the bridge bond's attributes to be copied to the array at the bridge index. The second occurrence of a bridge causes the entry to be removed. The attributes stored in the entry are then compared with those of the current bridge bond. If the two sets of attributes are incompatible, an error must be reported.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Testing bridge bond compatibility.}
    \label{fig:testing-bridge-bond-compatibility}
\end{figure}

>>>>

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a stack (Figure~\ref{fig:stack}). At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{stack.pdf}
    \caption{Stack for branches.}
    \label{fig:stack}
\end{figure}

Additional modifications allow bridge bonds to be tested for \textit{compatibility} (Figure~\ref{fig:bridge-bond-compatibility}). Compatibility is tested by comparing the attributes of each bridge bond. This test has three parts:

@@

A workflow modification allows bridge bonds to be compared for compatibility. A 100-element array is used to maintain state. The first occurrence of a bridge causes the bridge bond's attributes to be copied to the array at the bridge index. The second occurrence of a bridge causes the entry to be removed. The attributes stored in the entry are then compared with those of the current bridge bond. If the two sets of attributes are incompatible, an error must be reported.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{brdige-bond-compatibility.pdf}
    \caption{Bridge bond compatibility. Two bonds with the types indicated along the row and column headings are either compatible (green check marks) or incompatible (red X).}
    \label{fig:bridge-bond-compatibility}
\end{figure}
